Revisiting~the~Classics: Online~RL~in~the~Programmable~Dataplane

### 2021-06-01 paper/paper.tex
An algorithm
Mother of god.

\begin{algorithm}
	\caption{ParSa---\emph{Par}allel \emph{Sa}rsa\label{alg:parsa}}
	\SetKwProg{generate}{Function \emph{generate}}{}{end}

	Map store=new Map(obj, queue)\;
	\generate{Object pivot}{
		\ForAll{child $c$ in pivot}{
			\If{ $c$'s FieldContext is not set and $c$ is fusible}{
				generate($c$)\;
			}
		}
		build pivot's fieldContext $fc$\;
		EmitClassName\;
		EmitFields($fc$)\;
		EmitMethods($fc$)\;
	}
\end{algorithm}

@@

>>>>

\begin{algorithm}
	\caption{ParSa---\emph{Par}allel \emph{Sa}rsa\label{alg:parsa}}
	\SetKw{Let}{let}
	\SetKw{Enum}{enum}
	\SetKw{In}{in}
	\SetKw{Await}{await}
	\SetKw{Const}{const}
	\SetKwProg{parsa}{Function \emph{ParSa}}{}{end}
	\SetKwProg{control}{Function \emph{Ctl}}{}{end}
	\SetKwProg{minion}{Function \emph{Minion}}{}{end}
	\SetKwProg{tilecode}{Function \emph{TileCode}}{}{end}

	\tcc{Given message passing mechanisms \emph{scatter} and \emph{recv}, quantised arithmetic functions $Q_\mathit{mul}$ and TileCode, and omitting schedule/config/precache updates.}

	\Enum Par \{ Act(\emph{state}), Upd(\emph{delta, action, state}) \}\;
	\Const \emph{cfg, policy} = /* ... */\;
	\Let \emph{values}: [AtomicI32; cfg.n\_actions] = \{0\}\;
	\Let \emph{acks}: AtomicI32 = 0\;
	\parsa{id, schedule}{
		\uIf{id==0}{
			\ForAll{state\_pkt \In \inring{}}{
				Ctl(state\_pkt)\;
			}
		}
		\Else{
			\While{true}{Minion(schedule[id - 1], recv())\;}
		}
	}

	\control{state}{
		\emph{values, acks} = \{0\}, scatter(Par::Act(\emph{state}))\;
		acquire slot for \outring, copy \emph{state} into slot\;
		\Await acks == \emph{cfg.n\_minions}\;
		\Let \emph{action} = argmax(\emph{values})\;
		write \emph{action} into \outring{} slot, enqueue\;
		\If{cfg.online}{
			\Let \emph{((l\_state, l\_act, l\_val), found\_s)} = \emph{cfg.lookup\_state\_from\_key(state)}\;
			\Let \emph{(reward, found\_r)} = \emph{cfg.lookup\_reward\_from\_key(state)}\;
			\If{found\_s \&\& found\_r}{
				\Let $\delta_t$ = $\mathit{reward} + Q_\mathit{mul}$(\emph{cfg}.$\gamma$, \emph{values}[\emph{action}]) $-$ \emph{l\_val}\;
				$\delta_t$ = $Q_\mathit{mul}$(\emph{cfg}.$\alpha$, $\delta_t$)\;
				\emph{acks} = 0, scatter(Par::Upd($\delta_t$, \emph{action}, \emph{state}))\;
				\Await acks == \emph{cfg.n\_minions}\;
			}
			\emph{cfg}.store\_state(\emph{state}, \emph{action}, \emph{values}[\emph{action}])\;
		}
	}

	\minion{tasks, msg}{
		\Switch{msg}{
		\uCase{Par::Act(\emph{s})}{
			\ForAll{task \In tasks}{
				\Let \emph{hit} = TileCode(\emph{s}, \emph{task})\;
				\For{i \In [0..cfg.n\_actions)}{
					\emph{values}[\emph{i}].atomic\_add(\emph{policy}[\emph{hit}][\emph{a}])\;
				}
			}
		}
		\uCase{Par::Upd($\delta$, \emph{a}, \emph{s})}{
			\ForAll{task \In tasks}{
				\Let \emph{hit} = TileCode(\emph{s}, \emph{task})\;
				\emph{policy}[\emph{hit}][\emph{a}] += $\delta$\;
			}
		}
		}
		acks.atomic\_add(1)\;
	}

%	\tilecode{state, task}{
%		\Let \emph{hit} = \emph{cfg}.get\_task(task)\;
%	}
\end{algorithm}

?? Where to mention that algo 1 omits epsilon greedy etc?

@@

?? Future directions; transfer learning between classical methods into faster offline-only?
